%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ABSTRACT 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter*{ABSTRACT}
\addcontentsline{toc}{chapter}{ABSTRACT} % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

\pagestyle{plain} % No headers, just page numbers
\pagenumbering{roman} % Roman numerals
\setcounter{page}{2}

\begin{center}
\pvamumanuscripttitle

\pvamugradmonth \hspace{2pt} \pvamugradyear

\pvamufullname, B.S., southwest university of science and technology;

Chair of Advisory Committee: Dr. Lei Huang 

\par\end{center}

\indent Seismic volume is a basic data structure that has been widely used in geophysical computing, as well as in big data analytics applications of petroleum industry. It has been well studied in High Performance Computing (HPC) platforms. However, a little study has been done in big data analytics platforms. In this paper, we present an efficient Distributed Seismic Data Analytics Toolkit that works on the popular Apache Spark big data analytics platform. The toolkit supports different ways of seismic volume data distributions, repartition, transposing, access, and data parallelism with a variety of parallel execution templates. This work studies the performance characteristics of these seismic volume data operations with different configurations, current status of this big data analytics cloud at PVAMU as well as our research plan for future work. The scalability and parallelism are the main characteristics of this platform.  


 

\pagebreak{}
