%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  New template code for TAMU Theses and Dissertations starting Fall 2012.  
%  For more info about this template or the 
%  TAMU LaTeX User's Group, see http://www.howdy.me/.
%
%  Author: Wendy Lynn Turner 
%	 Version 1.0 
%  Last updated 8/5/2012
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                           ACKNOWLEDGEMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter*{ACKNOWLEDGEMENTS}
\addcontentsline{toc}{chapter}{ACKNOWLEDGEMENTS}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

I would like to thank my advisor, professors, colleagues and friends who helped me a lot in the past two years. I cannot make it through and finish my thesis without their kind help.

First I want to thank my advisor Dr. Lei Huang, for giving me the chance to work in CloudComputing Lab and guiding my study and research in cloud computing, and thanks to Dr. Lin Li and Dr. Frizell for spending their time to refine my thesis which benefits me a lot in academic writing skills. Special thanks to Mr Ted Clee, for sharing his deep knowledge of seismic data analytics.

I also appreciate all my colleagues and classmates worked in the lab in the past two years, for sharing so many interesting things from different cultures, and, of course, for helping and encouraging each other in research work.

Last but not least, I want to thank my friend Yuzhong Yan, for always being the guy helps me out at so many tough time in my life. I have learned so much from him not only as an engineer but also as a kind and wise man. 

\pagebreak{}

\ifx true false
\vspace*{\fill}
\begin{center}
A.M.D.G.
\end{center}
\vspace*{\fill}
\pagebreak{}
\fi
