\chapter*{CURRICULUM VITA}
\addcontentsline{toc}{chapter}{VITA}  % Needs to be set to part, so the TOC doesnt add 'CHAPTER ' prefix in the TOC.

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.

% Set your name here
\def\name{Chao Chen}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

% Place name at left
\section*{\large \bf \name}
\begin{singlespace}

\begin{minipage}{0.45\linewidth}
  Prairie View A\&M University \\
  Department of Computer Science \\
  P.O. Box 519, Prairie View, 77446
\end{minipage}
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{ll}
    Phone: & (832) 910-4615 \\
    Email: & \url{cchen.rough@gmail.com} \\
  \end{tabular}
\end{minipage}


\section*{\large \bf Education}

\begin{itemize}
  \item M.S. Computer Science, Prairie View A\&M University, 2016.

  \item B.A. Electronic Information Engineering, Southwest University of Science and Technology, 2005.

\end{itemize}

\section*{\large \bf Employment}

\begin{itemize}
\item Prairie View A\&M University, Research Assitant, 2015--2016.
\item Sunmedia Technology, Software Engineer, 2006--2014.
\end{itemize}


\section*{\large \bf Professional Skills}
\begin{itemize}
\item Solid background of computer science and software engineering, as well as strong learning and communication ability.
\item Proficient at Linux, Android and Embedded OS development, strong products development experiences including digital camera, digital photo frame and tablet.
\item Familiar with big data and cloud computing platform (Hadoop, Spark).
\end{itemize}



\section*{\large \bf Publications \& Achievements}

%\subsection*{Journal Articles}

\begin{itemize}

\item A Scalable and Productive Workflow-based Cloud Platform for Big Data Analytics, {\it 2016 IEEE International Conference on Big Data Analysis}, (ICBDA 2016) Hangzhou, China, March 12-14, 2016

\item A Productive Cloud Computing Platform Research for Big Data Analytics, {\it In Proc. of IEEE CloudCom 2015}, Nov 30-Dec 3, Vancouver, Canada

\end{itemize}

\end{singlespace}

% Footer
%\begin{center}
%  \begin{footnotesize}
%    Last updated: \today \\
%  \end{footnotesize}
%\end{center}



